Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for Policy Response Under Climate Change

### 2020-08-27 Scripts/Initial_Analysis.Rmd
Finalized Figure 3 for draft

ggplot(subset(Eez_d_hist, tresh == "Tresh_one")) +
  geom_density(
    aes(
      x = value,
      fill = tresh
    ),
    bins = 10,
    alpha = 0.8
  ) +
  facet_wrap(~metric,
             scales = "free") +
  scale_fill_viridis(discrete = T) +
  my_ggtheme_p() +
  ggsave("./Figures/hist_mean.png",
         width = 6,
         height = 6,
         units = "in"
  )

World_map_nemer <- World_map %>%
  left_join(Value_map_data,
            by = c("sau_fishing_entity","fishing_entity_id")
  )

grey_land <- World_map %>% 
  filter(!fishing_entity_id %in% World_map_nemer$fishing_entity_id)

@@

  tresh_list <- c("Tresh_one","Tresh_two")
  name_save <- paste("./Figures/emer_map_rev_",tresh_list[i],".png",sep = "")

@@

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            aes(fill = participation+2000),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    geom_sf(data = grey_land, aes(),fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(),fill = "grey50", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text", 
             x =-130,
             y = -69,
             label = "Participation (USD)", 
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-73,-34,5,45,83),
             y = -69,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set ToE labels
    annotate("text", 
             x =-130,
             y = -85,
             label = "Time of Emergence",
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-77,-37,3,42,82),
             y = -85,
             label = seq(2100,2000,-25), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis("",
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = c("","","","","")#,
      # direction = -1
    ) +
    my_ggtheme_m() +
    theme(
      legend.box.margin = margin(t = -66, l = 250),
      legend.text = element_blank(),
      legend.key.width = unit(5, "line"),
      axis.text = element_text(colour = "blue")
    ) +
    # guides(fill = guide_legend(nrow = 1))+
    ggsave(name_save,
           width = 12,
           height = 6,
           units = "in"
    )

>>>>

World_map_nemer <- World_map %>%
  left_join(Value_map_data,
            by = c("sau_fishing_entity","fishing_entity_id")
  ) %>% 
  filter(!is.na(participation))

grey_land <- World_map %>% 
  filter(!fishing_entity_id %in% World_map_nemer$fishing_entity_id) %>% 
  filter(sovereignt != "Antarctica")

@@

  tresh_list <- c("Tresh_one","Tresh_two")
  name_save <- paste("./Figures/emer_map_lat_",tresh_list[i],".png",sep = "")

  ## --------------- ##
  # Latitudinal plot
  ## --------------- ##

Eez_hist <- Eme_Res %>% 
  group_by(eezid,eez_name = sf_eez_name) %>% 
  left_join(Eez_centroid) %>% 
  filter(tresh == tresh_list[i]) %>% 
  group_by(latitude) %>% 
  summarise(
    number = n()
  ) %>% 
  group_by() %>% 
  mutate(RMean = rollmean(x = number, 
                          10, 
                          align = "center", 
                          fill = number
  )
  ) %>% 
  mutate(lab="lab") %>% 
  ggplot() +
  geom_area(
    aes(
      x = latitude,
      y = RMean,
      fill = lab,
      color = lab
    )
  ) +
  coord_flip() +
  scale_x_continuous("",
    limits = c(-50,80),
    breaks = c(-50,0,50,80)
  ) +
  scale_y_continuous(
    "Emerging stocks",
    limits = c(0, 124),
    breaks = c(0,62,124)

  ) +
  scale_fill_viridis(option="magma", discrete = T, begin = 0.7) +
  scale_color_viridis(option="magma", discrete = T, begin = 0.7) +
  theme_minimal() + 
  theme(
    panel.background = element_rect(fill = "white", colour = "white"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text = element_text(size = 12, colour="black"),
    axis.title.x = element_text(size = 12, colour="black", face = "bold"),
    legend.position = ""
  );Eez_hist

  ## --------------- ##
  # Map
  ## --------------- ##

@@

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            aes(fill = participation+2000),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    geom_sf(data = grey_land, aes(),fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(),fill = "grey50", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text", 
             x =-135,
             y = -69,
             label = "Participation (%)", 
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-76,-35,6,48,88),
             y = -69,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set ToE labels
    annotate("text", 
             x =-135,
             y = -85,
             label = "Time of Emergence",
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-79,-39,3,45,87),
             y = -85,
             label = seq(2100,2000,-25), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis("",
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = c("","","","","")#,
      # direction = -1
    ) +
    # geom_hline(yintercept = c(-50,0,50,80)) +
    my_ggtheme_m() +
    theme(
      legend.box.margin = margin(t = -64, l = 229),
      legend.text = element_blank(),
      legend.key.width = unit(5, "line")
    )

  ## --------------- ##
  # Combine plots and save them
  ## --------------- ##

  p <- ggdraw() +
    # ToE Latitudinal plot
    draw_plot(Eez_hist, x = 0.873, y = 0.13, width = 0.124, height = 0.77) +
    # Time of Emergence Map
    draw_plot(map, x = 0, y = 0, width = 0.95, height = 1)

  save_plot(
    name_save,
    p,
    base_height = 6,
    base_width = 12
  )

### 2020-08-27 Scripts/Manuscript.Rmd
Finalized Figure 3 for draft

```{r SSR_gain, eval = F,  echo = F, fig.width=9, fig.height=12, fig.cap =  "Average transboundary species SSR gain of neighbouring EEZs by 2030 (2021-2040) relative to 1951-2005 under RCP 8.5. Arrows go from the loosing EEZ (point) to the winner (arrowhead)"}

@@

![Average transboundary species SSR gain of neighbouring EEZs by 2030 (2021-2040) relative to 1951-2005 under RCP 8.5. Arrows go from the loosing EEZ (point) to the winner (arrowhead)](../Figures/Fig2.png)

@@

>>>>

```{r SSR_gain_map, eval = F,  echo = F, fig.width=9, fig.height=12, fig.cap =  "Average gain of transboundary stock share ratio (lines) and number of shifting stocks (polygon) by 2030 (2021-2040) relative to 1951-2005. Arrows go from the losing EEZ (point) to the winner. (arrowhead)"}

@@

![Average gain of transboundary stock share ratio (lines) and number of shifting stocks (polygon) by 2030 (2021-2040) relative to 1951-2005. Arrows go from the losing EEZ (point) to the winner. (arrowhead)](../Figures/Fig2.png)

@@

```{r Toe_map, eval = F,  echo = F, fig.width=9, fig.height=12, fig.cap =  ""}

img <- readPNG("../Figures/Fig3.png")
grid.raster(img)

![(Average time of emergence (ToE) per Exclusive Economic Zone (EEZ polygon) and participation of emerging stocks in total EEZ fishing revenue (land polygon). Darker tones represent low participation and late ToE; lighter colors represent large participation and earlier ToE. Density plot on right shows the number of emerging stocks across EEZ centroids (10^o running mean))](../Figures/Fig3.png)
